### 2019-03-11 manuscript/main.tex
- acknowledgments addition
- funding sources wording addition

%B: Perhaps other's funding sources for max BSF/NSF payoff? I added ours; no harm, I presume. 
NSF DEB-1655692 to BI, and DEB-1655478 to EEG.
The Minnesota Supercomputing Institute (MSI) at the University of Minnesota provided computing resources for this project.

>>>>

This work was supported by the National Science Foundation (DEB-1655692 to BI, and DEB-1655478 to EEG) and
the Minnesota Supercomputing Institute (MSI) at the University of Minnesota, which provided computing resources for this project.
%BI would like to thank SCHB for inspiration, sparring, and encouragement; maybe EEG, as well?
